---
title: "Examine partial net"
author: "Lasse Hjorth Madsen"
editor: source
date: "today"
toc: true
execute:
  echo: true
  warning: false
  cache: false
format:
  html:
    code-fold: true  
    code-tools: true
    df-print: paged
---

# Examine some networks

We collected a couple of nets, some converged in a reasonably about of time, some didn't. I'm wondering how they're different and if I can draw any conclusions about the best settings. And perhaps if the current algoritm is good or should be tweaked.

I'm looking at:

- **net1**, the currently published one. As I remember, it ran for a couple of days before converging. Likely an absolute threshold of 40. (Threshold means the number of followers you must have, *within* the network, to be included.)

- **net2** ran for ~48 hours without converging, collected a lot more connections, but a lot fewer members. I guess this means that people have many more connections, but not necessarily within the science community, meaning that it takes longer time to identify our network of interest.

- **net3**, however, ran for ~60 hours without converting, this time using a relative threshold of 0.005. Again a lot more connections, almost as many members as net1. Consistent with the idea that people have more connections.

- **net4** converged after ~5 hours, with a relative threshold of 0.05, so much more restrictive. It is also a lot smaller.

- **net5** converged after ~12 hours, with a compromise threshold of 0.03 

- **net6** finished after ~32 hours, with a threshold of 0.01, by reaching 30 iterations, the maximum allowed for. (Maybe increase this.)

- **net7** finished after ~24 hours, with a threshold of 0.01, after 46. (Wonder why this was quicker that net6?)

Relative thresholds in summary: 0.005 took forever; 0.05 took about 6h to converge; 0.03 about 12h; let's try maybe 0.01 or 0.02.


```{r setup}
#| echo: false
#| cache: false
library(tidyverse)
library(igraph)
devtools::load_all("../../blueskynet")
```


```{r get_token}
password    <- Sys.getenv("BLUESKY_APP_PASS")
identifier  <- Sys.getenv("BLUESKY_APP_USER")
auth_object <- get_token(identifier, password)
token       <- auth_object$accessJwt
```


```{r get_data}
#| cache: false

# Get saved profiles
profiles <- readRDS("../data/research_profiles_2024-10-24.rds")

# Get saved net and profiles
net1 <- readRDS("../data/research_net_2024-10-31.rds")
net2 <- readRDS("../data/research_net_2025-04-23.rds")
net3 <- readRDS("../data/research_net_2025-04-25.rds")
net4 <- readRDS("../data/research_net_2025-04-28.rds")
net5 <- readRDS("../data/research_net_2025-04-30.rds")
net6 <- readRDS("../data/research_net_2025-05-02.rds")
net7 <- readRDS("../data/research_net_2025-05-09.rds")

nets <- list(net1, net2, net3, net4, net5, net6, net7)

names(nets) <- c("net1", "net2", "net3", "net4", "net5", "net6", "net7")

remove(net1, net2, net3, net4, net5, net6, net7)
```

All networks starts off with one account, rossdahlke.bsky.social, then add eligible follows iteratively. Glimpse of the four networks:

```{r glimpse}
nets |> map(slice_head, n = 5)
```

The log below shows that for net2 more and more 'prospects' are considered, but that does not always result in more members being added. So we must consider a lot of irrelevant prospects.

We probably should switch to a *relative* threshold of followers rather that the absolute threshold of 40 that we used for this. We can't have the algo running forever, and it makes more sense too: 40 followers is a lot in a small network, but not in a big one.

# Trimming

After the networks either converges, reaches the maximum number of iterations, or are interrupted, we *trim* them, iteratively removing any members that do not match the threshold criteria anymore. Any account added early may not still meet the followers threshold after the network is fully expanded.


```{r trim}
trims <- nets |> 
  map(\(x) trim_net(x, threshold = 40)) |> 
  map(\(x) add_count(x, follows_handle)) |> 
  map(\(x) mutate(x, frac = n / n_distinct(x$actor_handle)))
```

Let's compare the number of edges in all nets, trimmed and full versions, using an absolute threshold of 40 (like in net1):

```{r trimmed_nets_edges}
bind_rows(map_dfr(nets , nrow), 
          map_dfr(trims, nrow)) |> 
mutate(net_type = c("full", "trimmed")) |> 
select(net_type, everything())
```

Then, compare the number of distinct members in nets, trimmed and full versions:

```{r trimmed_nets_members}
bind_rows(map_dfr(nets , \(x) n_distinct(x$actor_handle)),
          map_dfr(trims, \(x) n_distinct(x$actor_handle))) |> 
mutate(net_type = c("full", "trimmed")) |> 
select(net_type, everything())
```

Up until net4 the trimmed versions have many fewer edges, but not a lot fewer members. What does that mean? Maybe that the trimming removed a few popular accounts with a lot of followers?

Net4, net5, and net6 all used a relative threshold and converged (or, in the case of net 6, reached the maximum number of iterations). Maybe this more restrictive criteria means than the trimming is redundant.

Lets see examples of accounts trimmed away in net1:

```{r net1_diffs}
#| cache: true
removed <- setdiff(nets$net1$actor_handle, trims$net1$follows_handle)
profiles <- get_profiles(removed, token)
```

```{r show_diffs}
#| column: page-right
profiles |> 
  select(-did, -avatar, -createdAt, -indexedAt, -banner) |> 
  slice_sample(n = 50) 
```

Lets examine the observed distribution of followers, absolute and relative. First the full networks, before trimming:

```{r calculate_thresholds}
#| cache: false
nets <- nets |> 
  map(\(x) add_count(x, follows_handle)) |> 
  map(\(x) mutate(x, frac = n / n_distinct(x$actor_handle)))
```

```{r summarise_threshold}
quantiles <- c(0, 0.05, 0.5, 0.95, 1)

metrics <- nets |> 
  map_dfr(\(x) reframe(x, quantile = quantiles,
                       n = quantile(n, quantiles),
                       frac = quantile(frac, quantiles),
                       ), 
          .id = "id") |> 
  mutate(across(frac, \(x) round(x, 4)))

metrics |> filter(quantile %in% c(0, 0.5, 1))
```

Perhaps a boxplot is better:

```{r boxplot_trimmed}
nets |> 
  bind_rows(.id = "net") |> 
  group_by(net) |> 
  #slice_sample(n = 1000) |> 
  distinct(follows_handle, .keep_all = T) |> 
  ungroup() |> 
  pivot_longer(cols = c(n, frac)) |> 
  ggplot(aes(x = net, y = value)) +
  geom_boxplot(outliers = FALSE) +
  facet_wrap(facets = vars(name), scales = "free_y")
```
Boxplot *after* trimming:

```{r boxplot_full}
trims |> 
  bind_rows(.id = "net") |> 
  group_by(net) |> 
  #slice_sample(n = 1000) |> 
  distinct(follows_handle, .keep_all = T) |> 
  ungroup() |> 
  pivot_longer(cols = c(n, frac)) |> 
  ggplot(aes(x = net, y = value)) +
  geom_boxplot(outliers = FALSE) +
  facet_wrap(facets = vars(name), scales = "free_y")
```

# Densities

How about graph densities?

"The density of a graph is the ratio of the actual number of edges and the largest possible number of edges in the graph, assuming that no multi-edges are present." From [igraph](https://r.igraph.org/reference/edge_density.html) documentation.

```{r graph_density}
graphs <- nets |> map(as_tbl_graph)
graphs_trimmed <- trims |> map(as_tbl_graph)
```

Note that a graph can have loops -- when an account follow oneself. The full nets:

```{r loops}
graphs |> map_lgl(any_loop)
```

The trimmed versions:

```{r loops_trimmed}
graphs_trimmed |> map_lgl(any_loop)
```

```{r compare_densities}
bind_rows(map_dfr(graphs, edge_density, loops = TRUE),
          map_dfr(graphs_trimmed, edge_density, loops = TRUE)) |> 
mutate(net_type = c("full", "trimmed")) |> 
select(net_type, everything())
```

The trimmed versions have much higher density (as expected) except for net4. Also, the density for the partially completed nets (net2, net3) is lower. Finally, the density of the newer nets, trimmed version, seems to have increased since the oldest one.


# Output log, threshold = 40

Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Initial network: Number of actors : 1 Number of follows : 4149 Number of connections: 4149

Expanding the network, iteration number: 1 Number of prospects meeting the followers threshold of 40: 4148 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 3528 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2245

Updated network: Number of actors : 2246 Number of follows : 495875 Number of connections: 2562201

Time difference of 2.066851 hours

Expanding the network, iteration number: 2 Number of prospects meeting the followers threshold of 40: 10063 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 7694 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 1822

Updated network: Number of actors : 4068 Number of follows : 719183 Number of connections: 5075777

Time difference of 2.467354 hours

Expanding the network, iteration number: 3 Number of prospects meeting the followers threshold of 40: 21659 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 16101 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 1944

Updated network: Number of actors : 6012 Number of follows : 950092 Number of connections: 7622092

Time difference of 3.034004 hours

Expanding the network, iteration number: 4 Number of prospects meeting the followers threshold of 40: 30664 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 21907 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 1990

Updated network: Number of actors : 8002 Number of follows : 1168113 Number of connections: 10254793

Time difference of 3.41239 hours

Expanding the network, iteration number: 5 Number of prospects meeting the followers threshold of 40: 39563 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 27530 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 1530

Updated network: Number of actors : 9532 Number of follows : 1542540 Number of connections: 12885971

Time difference of 3.871151 hours

Expanding the network, iteration number: 6 Number of prospects meeting the followers threshold of 40: 46412 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 31400 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2307

Updated network: Number of actors : 11839 Number of follows : 1665064 Number of connections: 15497018

Time difference of 4.008213 hours

Expanding the network, iteration number: 7 Number of prospects meeting the followers threshold of 40: 53841 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 35343 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2681

Updated network: Number of actors : 14520 Number of follows : 1757259 Number of connections: 18158590

Time difference of 4.348331 hours

Expanding the network, iteration number: 8 Number of prospects meeting the followers threshold of 40: 61539 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 39251 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2813

Updated network: Number of actors : 17333 Number of follows : 1805579 Number of connections: 20649388

Time difference of 4.581201 hours

Expanding the network, iteration number: 9 Number of prospects meeting the followers threshold of 40: 68297 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 42228 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2514

Updated network: Number of actors : 19847 Number of follows : 1880854 Number of connections: 23216457

Time difference of 4.756973 hours

Expanding the network, iteration number: 10 Number of prospects meeting the followers threshold of 40: 74977 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 44806 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 2586

Updated network: Number of actors : 22433 Number of follows : 2045248 Number of connections: 25818519

Time difference of 4.952174 hours

Expanding the network, iteration number: 11 Number of prospects meeting the followers threshold of 40: 82108 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 47364 Getting follows ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of new actors with followers to add to network: 1561

Updated network: Number of actors : 23994 Number of follows : 2110453 Number of connections: 27307097

Time difference of 4.754154 hours

Expanding the network, iteration number: 12 Number of prospects meeting the followers threshold of 40: 86127 Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■ 100% \| ETA: 0s Number of valid prospects also matching the provided keywords: 48548 There were 50 or more warnings (use warnings() to see the first 50)h Getting follows ■■■■■■■■ 24% \| ETA: 8h

# Output log, threshold = 0.005

   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
Initial network:
   Number of actors     : 1
   Number of follows    : 4149
   Number of connections: 4149

Expanding the network, iteration number: 1
   Number of prospects meeting the followers threshold of 0.005: 4148
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 3527
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2436

Updated network:
   Number of actors     : 2437
   Number of follows    : 492228
   Number of connections: 2652314

Time difference of 2.06839 hours

Expanding the network, iteration number: 2
   Number of prospects meeting the followers threshold of 0.005: 37735
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 28125
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2189

Updated network:
   Number of actors     : 4626
   Number of follows    : 670762
   Number of connections: 5259818

Time difference of 3.868803 hours

Expanding the network, iteration number: 3
   Number of prospects meeting the followers threshold of 0.005: 38694
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 28153
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2062

Updated network:
   Number of actors     : 6688
   Number of follows    : 1013172
   Number of connections: 7914226

Time difference of 3.95644 hours

Expanding the network, iteration number: 4
   Number of prospects meeting the followers threshold of 0.005: 37987
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 26813
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2303

Updated network:
   Number of actors     : 8991
   Number of follows    : 1238562
   Number of connections: 10607249

Time difference of 3.751072 hours

Expanding the network, iteration number: 5
   Number of prospects meeting the followers threshold of 0.005: 36152
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 24927
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2160

Updated network:
   Number of actors     : 11151
   Number of follows    : 1424592
   Number of connections: 13293552

Time difference of 3.622893 hours

Expanding the network, iteration number: 6
   Number of prospects meeting the followers threshold of 0.005: 33989
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 22759
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2736

Updated network:
   Number of actors     : 13887
   Number of follows    : 1517094
   Number of connections: 16054728

Time difference of 3.43989 hours

Expanding the network, iteration number: 7
   Number of prospects meeting the followers threshold of 0.005: 30676
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 19684
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2314

Updated network:
   Number of actors     : 16201
   Number of follows    : 1724396
   Number of connections: 18679776

Time difference of 3.251576 hours

Expanding the network, iteration number: 8
   Number of prospects meeting the followers threshold of 0.005: 27999
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 17142
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1842

Updated network:
   Number of actors     : 18043
   Number of follows    : 2014392
   Number of connections: 21413013

Time difference of 3.103877 hours

Expanding the network, iteration number: 9
   Number of prospects meeting the followers threshold of 0.005: 26707
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 15597
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2597

Updated network:
   Number of actors     : 20640
   Number of follows    : 2086070
   Number of connections: 24175963

Time difference of 2.915274 hours

Expanding the network, iteration number: 10
   Number of prospects meeting the followers threshold of 0.005: 24253
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 13107
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2377

Updated network:
   Number of actors     : 23017
   Number of follows    : 2198819
   Number of connections: 26845533

Time difference of 2.754492 hours

Expanding the network, iteration number: 11
   Number of prospects meeting the followers threshold of 0.005: 21928
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 10829
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2280

Updated network:
   Number of actors     : 25297
   Number of follows    : 2302998
   Number of connections: 29550463

Time difference of 2.593921 hours

Expanding the network, iteration number: 12
   Number of prospects meeting the followers threshold of 0.005: 19968
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 8825
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2439

Updated network:
   Number of actors     : 27736
   Number of follows    : 2408573
   Number of connections: 32236915

Time difference of 2.443228 hours

Expanding the network, iteration number: 13
   Number of prospects meeting the followers threshold of 0.005: 17948
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 6747
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1690

Updated network:
   Number of actors     : 29426
   Number of follows    : 2750869
   Number of connections: 34755051

Time difference of 2.352025 hours

Expanding the network, iteration number: 14
   Number of prospects meeting the followers threshold of 0.005: 16619
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 5413
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1963

Updated network:
   Number of actors     : 31389
   Number of follows    : 2929731
   Number of connections: 37426028

Time difference of 2.233031 hours

Expanding the network, iteration number: 15
   Number of prospects meeting the followers threshold of 0.005: 15338
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 4065
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1825

Updated network:
   Number of actors     : 33214
   Number of follows    : 3023328
   Number of connections: 40064695

Time difference of 2.144277 hours

Expanding the network, iteration number: 16
   Number of prospects meeting the followers threshold of 0.005: 14237
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 2873
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1141

Updated network:
   Number of actors     : 34355
   Number of follows    : 3099298
   Number of connections: 42677159

Time difference of 2.108958 hours

Expanding the network, iteration number: 17
   Number of prospects meeting the followers threshold of 0.005: 14370
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 2624
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1216

Updated network:
   Number of actors     : 35571
   Number of follows    : 3147708
   Number of connections: 45272189

Time difference of 2.081526 hours

Expanding the network, iteration number: 18
   Number of prospects meeting the followers threshold of 0.005: 14967
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 2430
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 803

Updated network:
   Number of actors     : 36374
   Number of follows    : 3208118
   Number of connections: 47922068

Time difference of 2.097866 hours

Expanding the network, iteration number: 19
   Number of prospects meeting the followers threshold of 0.005: 17272
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 2578
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 671

Updated network:
   Number of actors     : 37045
   Number of follows    : 3248302
   Number of connections: 50602094

Time difference of 2.056244 hours

Expanding the network, iteration number: 20
   Number of prospects meeting the followers threshold of 0.005: 21708
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 3092
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 451

Updated network:
   Number of actors     : 37496
   Number of follows    : 3342454
   Number of connections: 53202643

Time difference of 2.168681 hours

Expanding the network, iteration number: 21
   Number of prospects meeting the followers threshold of 0.005: 26803
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 3836
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 471

Updated network:
   Number of actors     : 37967
   Number of follows    : 3434725
   Number of connections: 55899297

Time difference of 2.220064 hours

Expanding the network, iteration number: 22
   Number of prospects meeting the followers threshold of 0.005: 31459
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 4455
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 233

Updated network:
   Number of actors     : 38200
   Number of follows    : 3478640
   Number of connections: 58603976

Time difference of 2.268796 hours

Expanding the network, iteration number: 23
   Number of prospects meeting the followers threshold of 0.005: 36335
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 5204
There were 50 or more warnings (use warnings() to see the first 50)d
   Getting follows  ■■                                 5% | ETA:  2d

# Output log, threshold = 0.01 

> research_bundle <- build_network(key_actor = key_actor,
+                                  keywords = keywords,
+                                  token = token,
+                                  refresh_tok = refresh_tok,
+                                  threshold = threshold,
+                                  save_net = TRUE,
+                                  max_iterations = 30,
+                                  sample_size = Inf,
+                                  file_name = net_file,
+                                  prop = 1)
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
Initial network:
   Number of actors     : 1
   Number of follows    : 4149
   Number of connections: 4149

Expanding the network, iteration number: 1
   Number of prospects meeting the followers threshold of 0.01: 4148
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 3527
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2492

Updated network:
   Number of actors     : 2493
   Number of follows    : 389441
   Number of connections: 2601666

Time difference of 2.07896 hours

Expanding the network, iteration number: 2
   Number of prospects meeting the followers threshold of 0.01: 19927
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 15202
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1883

Updated network:
   Number of actors     : 4376
   Number of follows    : 678607
   Number of connections: 5157424

Time difference of 3.496401 hours

Expanding the network, iteration number: 3
   Number of prospects meeting the followers threshold of 0.01: 19753
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 14742
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1531

Updated network:
   Number of actors     : 5907
   Number of follows    : 1096868
   Number of connections: 7588008

Time difference of 3.868262 hours

Expanding the network, iteration number: 4
   Number of prospects meeting the followers threshold of 0.01: 18787
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 13592
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2088

Updated network:
   Number of actors     : 7995
   Number of follows    : 1207072
   Number of connections: 10061733

Time difference of 3.444768 hours

Expanding the network, iteration number: 5
   Number of prospects meeting the followers threshold of 0.01: 17142
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 11833
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1902

Updated network:
   Number of actors     : 9897
   Number of follows    : 1371305
   Number of connections: 12493187

Time difference of 3.250389 hours

Expanding the network, iteration number: 6
   Number of prospects meeting the followers threshold of 0.01: 15382
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 10006
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1830

Updated network:
   Number of actors     : 11727
   Number of follows    : 1513550
   Number of connections: 14946779

Time difference of 3.123755 hours

Expanding the network, iteration number: 7
   Number of prospects meeting the followers threshold of 0.01: 13493
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 8186
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 1777

Updated network:
   Number of actors     : 13504
   Number of follows    : 1716922
   Number of connections: 17337874

Time difference of 2.833329 hours

Expanding the network, iteration number: 8
   Number of prospects meeting the followers threshold of 0.01: 11634
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 6413
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2139

Updated network:
   Number of actors     : 15643
   Number of follows    : 1891207
   Number of connections: 19834141

Time difference of 2.318724 hours

Expanding the network, iteration number: 9
   Number of prospects meeting the followers threshold of 0.01: 9485
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 4322
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2641

Updated network:
   Number of actors     : 18284
   Number of follows    : 1956919
   Number of connections: 22589334

Time difference of 2.122224 hours

Expanding the network, iteration number: 10
   Number of prospects meeting the followers threshold of 0.01: 7140
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 2053
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 2018

Updated network:
   Number of actors     : 20302
   Number of follows    : 1989125
   Number of connections: 24429733

Time difference of 1.310837 hours

Expanding the network, iteration number: 11
   Number of prospects meeting the followers threshold of 0.01: 5509
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 561
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 529

Updated network:
   Number of actors     : 20831
   Number of follows    : 2003356
   Number of connections: 24984705

Time difference of 23.38069 mins

Expanding the network, iteration number: 12
   Number of prospects meeting the followers threshold of 0.01: 5187
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 246
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 214

Updated network:
   Number of actors     : 21045
   Number of follows    : 2006866
   Number of connections: 25187265

Time difference of 9.761754 mins

Expanding the network, iteration number: 13
   Number of prospects meeting the followers threshold of 0.01: 5081
   Number of valid prospects also matching the provided keywords: 140
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 108

Updated network:
   Number of actors     : 21153
   Number of follows    : 2009476
   Number of connections: 25343095

Time difference of 7.784276 mins

Expanding the network, iteration number: 14
   Number of prospects meeting the followers threshold of 0.01: 5080
   Number of valid prospects also matching the provided keywords: 129
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 98

Updated network:
   Number of actors     : 21251
   Number of follows    : 2010523
   Number of connections: 25465001

Time difference of 6.009215 mins

Expanding the network, iteration number: 15
   Number of prospects meeting the followers threshold of 0.01: 5091
   Number of valid prospects also matching the provided keywords: 144
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 113

Updated network:
   Number of actors     : 21364
   Number of follows    : 2014763
   Number of connections: 25645025

Time difference of 8.400094 mins

Expanding the network, iteration number: 16
   Number of prospects meeting the followers threshold of 0.01: 5122
   Number of valid prospects also matching the provided keywords: 180
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 148

Updated network:
   Number of actors     : 21512
   Number of follows    : 2016552
   Number of connections: 25862072

Time difference of 10.23027 mins

Expanding the network, iteration number: 17
   Number of prospects meeting the followers threshold of 0.01: 5119
   Number of valid prospects also matching the provided keywords: 209
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 177

Updated network:
   Number of actors     : 21689
   Number of follows    : 2018345
   Number of connections: 26072928

Time difference of 9.677389 mins

Expanding the network, iteration number: 18
   Number of prospects meeting the followers threshold of 0.01: 5130
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 218
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 185

Updated network:
   Number of actors     : 21874
   Number of follows    : 2020010
   Number of connections: 26258052

Time difference of 8.69139 mins

Expanding the network, iteration number: 19
   Number of prospects meeting the followers threshold of 0.01: 5111
   Number of valid prospects also matching the provided keywords: 195
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 163

Updated network:
   Number of actors     : 22037
   Number of follows    : 2020993
   Number of connections: 26416147

Time difference of 7.462659 mins

Expanding the network, iteration number: 20
   Number of prospects meeting the followers threshold of 0.01: 5076
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s
   Number of valid prospects also matching the provided keywords: 181
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 148

Updated network:
   Number of actors     : 22185
   Number of follows    : 2021773
   Number of connections: 26551391

Time difference of 7.025643 mins

Expanding the network, iteration number: 21
   Number of prospects meeting the followers threshold of 0.01: 5067
   Number of valid prospects also matching the provided keywords: 165
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 132

Updated network:
   Number of actors     : 22317
   Number of follows    : 2022680
   Number of connections: 26683944

Time difference of 6.360762 mins

Expanding the network, iteration number: 22
   Number of prospects meeting the followers threshold of 0.01: 5016
   Number of valid prospects also matching the provided keywords: 150
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 118

Updated network:
   Number of actors     : 22435
   Number of follows    : 2023464
   Number of connections: 26813609

Time difference of 6.345976 mins

Expanding the network, iteration number: 23
   Number of prospects meeting the followers threshold of 0.01: 5029
   Number of valid prospects also matching the provided keywords: 157
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 127

Updated network:
   Number of actors     : 22562
   Number of follows    : 2025296
   Number of connections: 26937511

Time difference of 6.089759 mins

Expanding the network, iteration number: 24
   Number of prospects meeting the followers threshold of 0.01: 5015
   Number of valid prospects also matching the provided keywords: 151
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 121

Updated network:
   Number of actors     : 22683
   Number of follows    : 2026146
   Number of connections: 27041645

Time difference of 4.971924 mins

Expanding the network, iteration number: 25
   Number of prospects meeting the followers threshold of 0.01: 5003
   Number of valid prospects also matching the provided keywords: 138
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 108

Updated network:
   Number of actors     : 22791
   Number of follows    : 2026837
   Number of connections: 27130125

Time difference of 4.311744 mins

Expanding the network, iteration number: 26
   Number of prospects meeting the followers threshold of 0.01: 4967
   Number of valid prospects also matching the provided keywords: 102
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 72

Updated network:
   Number of actors     : 22863
   Number of follows    : 2027270
   Number of connections: 27189012

Time difference of 3.13597 mins

Expanding the network, iteration number: 27
   Number of prospects meeting the followers threshold of 0.01: 4923
   Number of valid prospects also matching the provided keywords: 73
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 43

Updated network:
   Number of actors     : 22906
   Number of follows    : 2027502
   Number of connections: 27229555

Time difference of 2.364978 mins

Expanding the network, iteration number: 28
   Number of prospects meeting the followers threshold of 0.01: 4888
   Number of valid prospects also matching the provided keywords: 59
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 29

Updated network:
   Number of actors     : 22935
   Number of follows    : 2027756
   Number of connections: 27263627

Time difference of 2.079929 mins

Expanding the network, iteration number: 29
   Number of prospects meeting the followers threshold of 0.01: 4912
   Number of valid prospects also matching the provided keywords: 74
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 44

Updated network:
   Number of actors     : 22979
   Number of follows    : 2028120
   Number of connections: 27296487

Time difference of 2.071151 mins

Expanding the network, iteration number: 30
   Number of prospects meeting the followers threshold of 0.01: 4903
   Number of valid prospects also matching the provided keywords: 57
   Getting follows  ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% | ETA:  0s
   Number of new actors with followers to add to network: 27

Updated network:
   Number of actors     : 23006
   Number of follows    : 2028320
   Number of connections: 27319529

Time difference of 1.71364 mins
   Getting profiles ■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■■  100% |  ETA:  0s